Array Programming with NumPy

### 2020-06-03 body.tex
Minor fixes to response

NumPy also includes array-aware functions for creating, reshaping, concatenating, and padding
arrays; searching, sorting, and counting data; and reading and writing files.
It provides extensive support for generating pseudorandom numbers,
includes an assortment of probability distributions, and
performs accelerated linear algebra, utilizing one of several backends
such as OpenBLAS \cite{wang2013augem,xianyi2012model} or Intel MKL optimized
for the CPUs at hand.

@@

The developer culture has matured: while initial development was
highly informal, NumPy now has a roadmap and a process for proposing
and discussing large changes.  The project has formal governance
structures and is fiscally sponsored by NumFOCUS, a nonprofit that
promotes open practices in research, data, and scientific computing.
Over the past few years, the project attracted its first funded
development, sponsored by the Moore and Sloan Foundations, and
received an award as part of the Chan Zuckerberg Initiative's
Essentials of Open Source Software program.  With this funding, the
project was (and is) able to have sustained focus over multiple months
to implement substantial new features and improvements.  That said, it
still depends heavily on contributions made by graduate students and
researchers in their free time.

>>>>

NumPy also includes array-aware functions for creating, reshaping, concatenating, and padding
arrays; searching, sorting, and counting data; and reading and writing files.
It provides extensive support for generating pseudorandom numbers,
includes an assortment of probability distributions, and
performs accelerated linear algebra, utilizing one of several backends
such as OpenBLAS \cite{wang2013augem,xianyi2012model} or Intel MKL optimized
for the CPUs at hand (see Supplementary Methods for more details).

@@

The developer culture has matured: while initial development was
highly informal, NumPy now has a roadmap and a process for proposing
and discussing large changes.  The project has formal governance
structures and is fiscally sponsored by NumFOCUS, a nonprofit that
promotes open practices in research, data, and scientific computing.
Over the past few years, the project attracted its first funded
development, sponsored by the Moore and Sloan Foundations, and
received an award as part of the Chan Zuckerberg Initiative's
Essentials of Open Source Software program.  With this funding, the
project was (and is) able to have sustained focus over multiple months
to implement substantial new features and improvements.  That said, it
still depends heavily on contributions made by graduate students and
researchers in their free time (see Supplementary Methods for more details).
